Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-11-01 paper/paper.tex
More
Start on VF2 kr

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[every node/.style={inner sep=0pt, outer sep=0pt}]
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(10, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(20, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(30, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-30-150.pdf}}; &
            \\
        };
    \end{tikzpicture}

>>>>

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[every node/.style={inner sep=0pt, outer sep=0pt}]
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(10, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(20, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \node [anchor=center] {\scriptsize $\mathcal{G}(30, x){\rightarrowtail}\mathcal{G}(150, y)$}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-satisfiable-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-kr-nodes-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize LAD}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-kr-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-kr-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-kr-nodes-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize VF2}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-kr-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-kr-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-kr-nodes-30-150.pdf}}; &
            \\
        };
    \end{tikzpicture}
